\textbf{Best practices for applying machine learning to bacterial 16S rRNA gene sequencing data}

### 2019-07-18 submission/manuscript.Rmd
add a Table 1

\newpage
\includegraphics{TableS1.pdf}
**Table S1. ML model complexity and hyperparameter range.** 
\newpage

>>>>

\newpage
\captionof{table}{Characteristics of the machine learning models in our comparative study.}
\small
\begin{tabular}{|l|l|l|l|l|}
\hline
\rowcolor{lightgray}
\textbf{Model} & \textbf{Description} & \textbf{Linearity} & \textbf{Interpretability} & \textbf{Refs.} \\ \hline
\makecell[l]{Logistic \\regression} & \makecell[l]{A predictive regression analysis when the dependent \\variable is binary.} & Linear & Interpretable & $^{36}$\\ \hline
\makecell[l]{SVM with \\linear kernel} & \makecell[l]{A classifier that is defined by an optimal linear \\seperating hyperplane that discriminates between labels.} & Linear & Interpratable & $^{37}$\\ \hline
\makecell[l]{SVM with \\radial basis kernel} & \makecell[l]{A classifier that is defined by an optimal gaussian \\seperating hyperplane that discriminates between labels.} & Non-linear & Explainable$^*$ & $^{38}$\\ \hline
Decision tree & \makecell[l]{A classifier that sorts samples down from the 
root to the \\leaf node where an attribute is tested to discriminate \\between labels} & Non-linear & Interpretable & $^{39}$\\ \hline
Random forest & \makecell[l]{A classifier that is a decision tree ensemble that \\grow randomly with subsampled data.} & Non-linear & Explainable$^*$ & $^{40-41}$  \\ \hline
XGBoost & \makecell[l]{A classifier that is a decision tree ensemble that \\grow with additive training.} & Non-linear & Explainable$^*$ & $^{42-43}$ \\ \hline
\end{tabular}
\begin{tablenotes}\footnotesize
\item[1]{$^*$Explainable models are not inherently interpretable but can be explained with post-hoc analyses.}
\end{tablenotes}
\newpage

### 2019-07-18 submission/manuscript.tex
add a Table 1

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage[table]{xcolor}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{caption}

\usepackage{helvet} % Helvetica font
\renewcommand*\familydefault{\sfdefault} % Use the sans serif version of the font
\usepackage[T1]{fontenc}

@@

\includegraphics{TableS1.pdf} \textbf{Table S1. ML model complexity and
hyperparameter range.} \newpage

>>>>

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage[table]{xcolor}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{caption}
\usepackage{makecell}
\usepackage{threeparttable}

\usepackage{helvet} % Helvetica font
\renewcommand*\familydefault{\sfdefault} % Use the sans serif version of the font
\usepackage[T1]{fontenc}
\usepackage[labelfont=bf]{caption}

@@

\captionof{table}{Characteristics of the machine learning models in our comparative study.}
\small

\begin{tabular}{|l|l|l|l|l|}
\hline
\rowcolor{lightgray}
\textbf{Model} & \textbf{Description} & \textbf{Linearity} & \textbf{Interpretability} & \textbf{Refs.} \\ \hline
\makecell[l]{Logistic \\regression} & \makecell[l]{A predictive regression analysis when the dependent \\variable is binary.} & Linear & Interpretable & $^{36}$\\ \hline
\makecell[l]{SVM with \\linear kernel} & \makecell[l]{A classifier that is defined by an optimal linear \\seperating hyperplane that discriminates between labels.} & Linear & Interpratable & $^{37}$\\ \hline
\makecell[l]{SVM with \\radial basis kernel} & \makecell[l]{A classifier that is defined by an optimal gaussian \\seperating hyperplane that discriminates between labels.} & Non-linear & Explainable$^*$ & $^{38}$\\ \hline
Decision tree & \makecell[l]{A classifier that sorts samples down from the 
root to the \\leaf node where an attribute is tested to discriminate \\between labels} & Non-linear & Interpretable & $^{39}$\\ \hline
Random forest & \makecell[l]{A classifier that is a decision tree ensemble that \\grow randomly with subsampled data.} & Non-linear & Explainable$^*$ & $^{40-41}$  \\ \hline
XGBoost & \makecell[l]{A classifier that is a decision tree ensemble that \\grow with additive training.} & Non-linear & Explainable$^*$ & $^{42-43}$ \\ \hline
\end{tabular}\begin{tablenotes}\footnotesize
\item[1]{$^*$Explainable models are not inherently interpretable but can be explained with post-hoc analyses.}
\end{tablenotes}\newpage
